---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
#CIDR - Clustering through Imputation and Dimensionality Reduction

Fast and accurate clustering through imputation and dimensionality
reduction for Single Cell RNA-seq data.

Most existing dimensionality reduction and clustering packages for single cell RNA-Seq (scRNA-
Seq) data deal with dropouts by heavy modelling and computational machinery. Here we in-
troduce _CIDR_ (Clustering through Imputation and Dimensionality Reduction), an ultrafast
algorithm which uses a novel yet very simple ‘implicit imputation’ approach to alleviate the
impact of dropouts in scRNA-Seq data in a principled manner.

##Getting Started

* Make sure your version of R is at least 3.1.0
* If you are on the Windows platorm, ensure that [Rtools](https://cran.r-project.org/bin/windows/Rtools/) is installed
* install the _devtools_ package which will be used to install _CIDR_ and its dependencies:
```{r, eval=F}
install.packages("devtools")
```

* Install the _CIDR_ package directly from the Github repository (including any dependencies):

```{r, eval=F}
devtools::install_github("VCCRI/CIDR")
```

#Example
Test the newly installed _CIDR_ package:

```{r}
library(cidr)
example("cidr")
```
