---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
#CIDR - Clustering through Imputation and Dimensionality Reduction

Fast and accurate clustering through imputation and dimensionality
reduction for single cell RNA-seq data.

Most existing dimensionality reduction and clustering packages for single cell RNA-Seq (scRNA-Seq) data deal with dropouts by heavy modelling and computational machinery. Here we introduce _CIDR_ (Clustering through Imputation and Dimensionality Reduction), an ultrafast
algorithm which uses a novel yet very simple ‘implicit imputation’ approach to alleviate the
impact of dropouts in scRNA-Seq data in a principled manner.

##Getting Started

* Make sure your version of R is at least 3.1.0
* _CIDR_ has been tested primarily on the Linux and Mac platforms.  _CIDR_ has also been tested on the Windows platform - however this requires the use of an external software package _Rtools_.
* If you are on the Windows platorm, ensure that [Rtools](https://cran.r-project.org/bin/windows/Rtools/) is installed. Rtools is software (installed external to R) that assists in building R packages, and R itself.  Note that the downlaod for _Rtools_ is in the order of 100M.
* install the CRAN package _devtools_ package which will be used to install _CIDR_ and its dependencies:
```{r, eval=F}
## this is an R command
install.packages("devtools")
```

* Install the _CIDR_ package directly from the Github repository (including any dependencies):

```{r, eval=F}
## this is an R command
devtools::install_github("VCCRI/CIDR")
## Note that for some Windows platforms, you may be asked to re-install RTools
## - even though it may already have been installed.  Say yes if prompted.
## Your windows platform may require the specific version of RTools being suggested.
```

#Example
Test the newly installed _CIDR_ package:

```{r}
library(cidr)
example("cidr")
```
